Algorithmic Approaches to Match Degraded Land Impressions

### 2017-10-22 degraded-paper.tex
Rebuild the pdf I guess

\begin{figure}[htbp]
\centering
\includegraphics{degraded-paper_files/figure-latex/roughcordist-1.pdf}
\caption{\label{fig:roughcordist}Empirical CDFs of the Roughness Correlation
compared to the CCF for known matches and known non-matches. It can be
seen that the distribution of each feature for the known non-matches is
quite symmetric, while the distribution for each feature for the known
matches is skewed left.}
\end{figure}

@@

\begin{table}[H]
\centering
\begin{tabular}{lr}
  \hline
Result & Count \\ 
  \hline
False Negative & 20.7 \\ 
  False Positive & 1.9 \\ 
  True Negative & 3716.8 \\ 
  True Positive & 56.5 \\ 
   \hline
\end{tabular}
\caption{The average confusion matrix for the 10 random forests. It can be seen that false positives are exceedingly rare, but false negatives occur more frequently.} 
\label{tab:avgforest}
\end{table}

@@

\begin{table}[H]
\centering
\begin{tabular}{lllll}
  \hline
Study & False Negative & False Positive & True Negative & True Positive \\ 
  \hline
Hamby252\_Hamby252 & 0.39\% & 0.02\% & 97.56\% & 2.03\% \\ 
  Hamby252\_Hamby44 & 0.45\% & 0.05\% & 98.31\% & 1.19\% \\ 
  Hamby44\_Hamby44 & 0.89\% & 0.09\% & 97.68\% & 1.34\% \\ 
   \hline
\end{tabular}
\caption{The average confusion matrix for the 10 random forests, broken down by study. It can be seen that Hamby252 to Hamby252 comparisons exhibit the fewest errors, while Hamby44 to Hamby44 comparisons exhibit the most on average.} 
\label{tab:avgforeststudy}
\end{table}

@@

\begin{table}[H]
\centering
\begin{tabular}{llll}
  \hline
Prediction $\backslash$ Actual & Hamby252\_Hamby252 & Hamby252\_Hamby44 & Hamby44\_Hamby44 \\ 
  \hline
Hamby252\_Hamby252 & 09.6\% & 08.32\% & 11.28\% \\ 
  Hamby252\_Hamby44 & 81.47\% & 81.06\% & 78.68\% \\ 
  Hamby44\_Hamby44 & 08.93\% & 10.63\% & 10.04\% \\ 
   \hline
\end{tabular}
\caption{Confusion Matrix (Column Proportions) for the random forest with study as the response. It can be seen that the random forest performs poorly, as hoped, indicating that a simple model to predict the study using the features available is not enough to detect the operator effects.} 
\label{tab:studypred}
\end{table}

>>>>

\begin{figure}
\includegraphics[width=.5\textwidth]{degraded-paper_files/figure-latex/roughcordist-1} \caption{Empirical CDFs of the Roughness Correlation compared to the CCF for known matches and known non-matches. It can be seen that the distribution of each feature for the known non-matches is quite symmetric, while the distribution for each feature for the known matches is skewed left.}\label{fig:roughcordist}
\end{figure}

@@

\begin{table}[H]
\centering
\begin{tabular}{lr}
  \hline
Result & Count \\ 
  \hline
False Negative & 20.6 \\ 
  False Positive & 2.0 \\ 
  True Negative & 3716.7 \\ 
  True Positive & 56.6 \\ 
   \hline
\end{tabular}
\caption{The average confusion matrix for the 10 random forests. It can be seen that false positives are exceedingly rare, but false negatives occur more frequently.} 
\label{tab:avgforest}
\end{table}

@@

\begin{table}[H]
\centering
\begin{tabular}{lllll}
  \hline
Study & False Negative & False Positive & True Negative & True Positive \\ 
  \hline
Hamby252\_Hamby252 & 0.38\% & 0.02\% & 97.56\% & 2.04\% \\ 
  Hamby252\_Hamby44 & 0.45\% & 0.05\% & 98.3\% & 1.19\% \\ 
  Hamby44\_Hamby44 & 0.88\% & 0.09\% & 97.68\% & 1.35\% \\ 
   \hline
\end{tabular}
\caption{The average confusion matrix for the 10 random forests, broken down by study. It can be seen that Hamby252 to Hamby252 comparisons exhibit the fewest errors, while Hamby44 to Hamby44 comparisons exhibit the most on average.} 
\label{tab:avgforeststudy}
\end{table}

@@

\begin{table}[H]
\centering
\begin{tabular}{llll}
  \hline
Prediction $\backslash$ Actual & Hamby252\_Hamby252 & Hamby252\_Hamby44 & Hamby44\_Hamby44 \\ 
  \hline
Hamby252\_Hamby252 & 09.93\% & 08.47\% & 011.3\% \\ 
  Hamby252\_Hamby44 & 81.24\% & 80.82\% & 78.27\% \\ 
  Hamby44\_Hamby44 & 08.83\% & 010.7\% & 10.43\% \\ 
   \hline
\end{tabular}
\caption{Confusion Matrix (Column Proportions) for the random forest with study as the response. It can be seen that the random forest performs poorly, as hoped, indicating that a simple model to predict the study using the features available is not enough to detect the operator effects.} 
\label{tab:studypred}
\end{table}
